---
title: "Assignment 5 - Meta-analysis of pitch in schizophrenia"
author: "Mie, Cecilie, Tobias and Josephine"
date: "4th of december 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Library 
library('pacman')
pacman::p_load(gdata,
               metafor,
               lme4,
               tidyverse,
               plyr,
               reshape2,
               data.table)

data <- readxl::read_xlsx("Matrix_MetaAnalysis_Diagnosis_updated290719.xlsx")

df <- data[,c(2, 21:22, 69:72)]
```

# Building on the shoulders of giants: meta-analysis

## Questions to be answered

1. What is the current evidence for distinctive vocal patterns in schizophrenia? Report how many papers report quantitative estimates, comment on what percentage of the overall studies reviewed they represent (see PRISMA chart) your method to analyze them, the estimated effect size of the difference (mean effect size and standard error) and forest plots representing it. N.B. Only measures of pitch mean and pitch sd are required for the assignment. Feel free to ignore the rest (although pause behavior looks interesting, if you check my article).

```{r}
#calculating the % of studies usable of the total 4341 studies 
# 6 usable studies out of 4341
6/4341*100 #0.138217 % ~ 0.14 %

#calculating yi and vi
PitchMeanES <- metafor::escalc(data = df,
                               measure = "SMD",
                               n1i = SAMPLE_SIZE_SZ,
                               n2i = SAMPLE_SIZE_HC,
                               m1i = PITCH_F0_SZ_M,
                               m2i = PITCH_F0_HC_M,
                               sd1i = PITCH_F0_SZ_SD,
                               sd2i = PITCH_F0_HC_SD)

#investigating the mean of the mean and the mean of the standard error
new_data <- subset(PitchMeanES, StudyID == 1| StudyID == 5|StudyID == 11|StudyID == 18|StudyID == 28|StudyID == 50)

mean(new_data$PITCH_F0_HC_M)
mean(new_data$PITCH_F0_SZ_M)

mean(new_data$PITCH_F0_HC_SD)
mean(new_data$PITCH_F0_SZ_SD)

# Creating a liniar mixed effect model for the data 
model <- lmer(data = PitchMeanES,
     na.action = "na.omit",
     yi ~ 1 + (1|StudyID),
     weights = 1 / vi,
     REML = FALSE,
     control = lmerControl(
         check.nobs.vs.nlev = "ignore",
         check.nobs.vs.nRE = "ignore"))

# creating a rma model to investigate the meta analysis
model <- rma(yi, vi, data = PitchMeanES, slab = StudyID)

#creating a forest plot
forest(model)

```


2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots.

``` {r}
# load A3 data
a3_data <- read.csv("C:/Users/Bruger/Documents/Experimental methods III/A3/pitch_data.csv", header = TRUE)

# summarize mean, sd and sample size by Study and Diagnosis
a3 <- a3_data %>%
    ddply(~Study + Diagnosis, summarise, mean=mean(mean), sd=mean(sd), sample_size=length(unique(Participant)))

# rename factor levels
a3$Diagnosis <- as.factor(a3$Diagnosis)
levels(a3$Diagnosis) <- c("HC", "SZ")

# convert to wide format
a3 <- dcast(setDT(a3), Study~Diagnosis, value.var=c("mean", "sd", "sample_size"))

# rename colnames to match the other data
a3$Study <- a3$Study + 57 # 48 studies in the other analysis, so avoid conflicting ID's
colnames(a3) <- c("StudyID",
                  "PITCH_F0_HC_M",
                  "PITCH_F0_SZ_M",
                  "PITCH_F0_HC_SD",
                  "PITCH_F0_SZ_SD",
                  "SAMPLE_SIZE_HC",
                  "SAMPLE_SIZE_SZ")

# bind together by columns
df_a3 <- rbind(df, a3)



# calculating the yi and the vi values for each study
PitchMeanES_a3 <- metafor::escalc(data = df_a3,
                               measure = "SMD",
                               n1i = SAMPLE_SIZE_SZ,
                               n2i = SAMPLE_SIZE_HC,
                               m1i = PITCH_F0_SZ_M,
                               m2i = PITCH_F0_HC_M,
                               sd1i = PITCH_F0_SZ_SD,
                               sd2i = PITCH_F0_HC_SD)

# creating a model for all studies 
model_a3 <- lmer(data = PitchMeanES_a3,
     na.action = "na.omit",
     yi ~ 1 + (1|StudyID),
     weights = 1 / vi,
     REML = FALSE,
     control = lmerControl(
         check.nobs.vs.nlev = "ignore",
         check.nobs.vs.nRE = "ignore"))

# rma model for all studies
model_a3 <- rma(yi, vi, data = PitchMeanES_a3, slab = StudyID)

#forest plot for all data
forest(model_a3)

# for only assignment 3
a3_info <- subset(PitchMeanES_a3, StudyID > 57)

#rma model for only assignment 3
model_a3_info <- rma(yi, vi, data = a3_info, slab = StudyID)

#forest plot for a3
forest(model_a3_info)

# summarising all the models
summary(model_a3_info)
summary(model)
summary(model_a3)
```

3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.

``` {r}
#focusing on model a3 for all studies 

# creating funnel plots
funnel(model)
funnel(model_a3)

#Rank test of model a3 
ranktest(model_a3)


# output of rma
model_a3 %>% summary()
model_a3
# tau =  0.455
# I^2 = 72.08%

# confident intervallerne 
confint(model_a3)

# influence plot
plot(influence(model_a3))

```

## Tips on the process to follow:

- Download the data on all published articles analyzing voice in schizophrenia and the prisma chart as reference of all articles found and reviewed
- Look through the dataset to find out which columns to use, and if there is any additional information written as comments (real world data is always messy!).
    * Hint: PITCH_F0M and PITCH_F0SD group of variables are what you need
    * Hint: Make sure you read the comments in the columns: `pitch_f0_variability`, `frequency`, `Title`,  `ACOUST_ANA_DESCR`, `DESCRIPTION`, and `COMMENTS`
- Following the procedure in the slides calculate effect size and standard error of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.
 . first try using lmer (to connect to what you know of mixed effects models)
 . then use rma() (to get some juicy additional statistics)

- Build a forest plot of the results (forest(model))
 
- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?

- Now look at the output of rma() and check tau and I2
